Exception Handling Bug Hazards in Android

### 2015-10-07 SPRINGER_JOURNAL/msr_journal.tex
survey section - new charts

\begin{figure} \centering \includegraphics[scale=0.63]{charts/often_new.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.57]{charts/summary_new.png}
\caption{Summary of some survey question answers. }
\label{fig:oftenhandle}
\end{figure}

@@

%//////NULLPONTER WORSE IN ANDROID /////
Developers were also asked whether or not craches caused by NullPointerException were most common in Android development than in stantard Java development.  Almost half of them (XXX\%) mentioned that Android apps were more suceptible to NullPointerException crashes. Some of the reasons mentioned by developers were: (i) the activity and fragment lifecycle - since both are constantly distroyed its references can frequently become null leading to NullPointerExceptions; (ii) the framework complexity - several methods od Android framework return null, and there is not enought documentation to inform the developer when using such methods.

>>>>

\begin{figure} \centering \includegraphics[scale=0.63]{charts/agree_new2.png}
\caption{How often developers throw and handle exceptions during app development.}
\label{fig:oftenhandle}
\end{figure}

\begin{figure} \centering \includegraphics[scale=0.57]{charts/yes_no_new2.png}
\caption{Summary of some survey question answers. }
\label{fig:oftenhandle}
\end{figure}

@@

%//////NULLPONTER WORSE IN ANDROID /////
Developers were asked if their apps ever crashed  because of a NullPointerException. The vast majority of respondents (96\%) said that their apps crashed at least once due to a NullPointerException. 
Their answers are aligned with the high prevalence of NullPointerExceptions found in the mining study - in Table XXX we can see that NullPointerExceptions were the main cause of the mined exception stack traces.
The developers were also asked whether or not craches caused by NullPointerException were most common in Android development than in stantard Java development.  Almost half of them (XXX\%) mentioned that Android apps were more suceptible to NullPointerException crashes. Some of the reasons mentioned by developers were: (i) the activity and fragment lifecycle - since both are constantly distroyed its references can frequently become null leading to NullPointerExceptions; (ii) the framework complexity - several methods od Android framework return null, and there is not enought documentation to inform the developer when using such methods.
